Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-15 manuscript.Rmd
actually run fake chunk to ensure correctness closes #275

```{r, eval=FALSE, echo=-1}
# this is a fake chunk, the faked output comes the chunk below
report_analysis(planned_analysis(simulate_data(900, 8, 0.3, 10)
```

>>>>

```{r, eval=TRUE, echo=-1, results='hide'}
# this is a fake chunk, the faked output comes the chunk below
report_analysis(planned_analysis(simulate_data(900, 8, 0.3, 10)))
```
